Toward nonlinear multigrid \\ for nonlinear and nonlocal variational inequalities

### 2023-02-09 talk/slides.tex
minimally acceptable talk

\begin{frame}{\alert{summary}}

\begin{itemize}
\item x
\end{itemize}
\end{frame}

>>>>

\begin{frame}{summary and outlook}

\begin{itemize}
\item the \alert{variational inequality (VI)} problem class is good to know
\item likewise \alert{full approximation storage (FAS) multigrid}
    \begin{itemize}
    \item[$\circ$] need for better support and documentation in PETSc/Firedrake
    \end{itemize}
\item multigrid treatment of nonlinear and \alert{nonlocal VIs}?
    \begin{itemize}
    \item[$\circ$] smoothers not obvious in nonlocal cases
    \item[$\circ$] seeking practical evidence of mesh-independent convergence
    \end{itemize}
\item glacier evolution, as fluid-layer-in-climate problems, \alert{needs attention} from applied mathematicians and numerical analysts
    \begin{itemize}
    \item[$\circ$] VI form not widely recognized
    \item[$\circ$] current state of the art $=$ explicit time stepping of surface
        \begin{itemize}
        \item[$\vartriangleright$] slow for science, intrinsically \emph{not} scalable
        \end{itemize}
    \item[$\circ$] to do: \alert{steady-state and implicit step VI problems}
    \item[$\circ$] more on this view in my Math.~Geosci.~seminar tomorrow 2pm L5
    \end{itemize}
\end{itemize}
\end{frame}
